---
title: "Resources"
author: "Zhen Li"
date: "2018-11-28"
output:
  blogdown::html_page:
    toc: true
---

```{r setup, echo=F}
knitr::opts_chunk$set(cache = TRUE)
setwd("~/zhen/scripts/zhenli.name2/content/")
library(DT)
library(openxlsx)
```


<!-- In this page, you will find various useful resources related to single cell genomics, including: -->

<!-- * [List of human neocortex single cell RNA-seq datasets](#anchor1) -->
<!-- * [List of human organoid single cell RNA-seq datasets](#anchor2) -->
<!-- * List of mouse single cell RNA-seq datasets -->
<!-- * List of single cell genomics datasets -->

# Single cell RNA-seq Datasets

## Human

```{r, message=F, warning=F, include=F, echo=F}
dt1 <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 1,rowNames = F)
d1 <- datatable(dt1, escape = F, extensions = "Responsive", options  = list(autoWidth = F))
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(htmlwidgets)
library(htmltools)

htmlwidgets::saveWidget(d1, file = "d1.html", selfcontained = TRUE)
```

<iframe seamless src="../d1/index.html" width="100%" height="500"></iframe>

## Mouse

```{r, message=F, warning=F, include=F, echo=F}
dt2 <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 2,rowNames = F)
d2 <- datatable(dt2, escape = F, extensions = "Responsive", options  = list(autoWidth = F))
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(htmlwidgets)
library(htmltools)

htmlwidgets::saveWidget(d2, file = "d2.html", selfcontained = TRUE)
```

<iframe seamless src="../d2/index.html" width="100%" height="500"></iframe>

## Human organoid
```{r, message=F, warning=F, include=F, echo=F}
dt3 <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 3,rowNames = F)
d3 <- datatable(dt3, escape = F, options  = list(autoWidth = F))
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(htmlwidgets)
library(htmltools)

htmlwidgets::saveWidget(d3, file = "d3.html", selfcontained = TRUE)
```

<iframe seamless src="../d3/index.html" width="100%" height="500"></iframe>

---

# Other resources
<div class="row">
<div class="column left">
<a href="http://www.brainspan.org/">BrainSpan</a>
</div>
<div class="column right">
<p>A large transcriptome database of the developing human brain.</p>
</div>
</div>
<div class="row">
<div class="column left">
<a href="http://hbatlas.org/mouseNCXtranscriptome/">Mouse Neocortical Transcriptome</a>
</div>
<div class="column right">
Atlas of gene expressions in mouse brain, including coding and some noncoding genes. It shows rough layer information.
</div>
</div>
<div class="row">
<div class="column left">
<a href="http://psychencode.org/">PsychENCODE</a>
</div>
<div class="column right">
Collection of data from the PsychENCODE consortium. This large dataset include RNA-seq, CHIP-seq, genomic sequencing and proteomics data of the developing human brain and numerous brain regions.
</div>
</div>
<div class="row">
<div class="column left">
<a href="https://david.ncifcrf.gov/">DAVID Gene Ontology</a>
</div>
<div class="column right">
Classic gene ontology analysis website.
</div>
</div>
